On the combination of Set Functions and Failures

### 2014-05-26 docs/src/usage.tex
Manual updated

>>>>

\item[\fbox{\code{parser $opts$}}]\pindex{parser}
Define additional options passed to the \CYS front end, i.e.,
the parser program \code{\cyshome/bin/cymake}.
For instance, setting the option
\begin{curry}
:set parser -F --pgmF=transcurry
\end{curry}
has the effect that each Curry module to be compiled is
transformed by the preprocessor command \code{transcurry}
into a new Curry program which is actually compiled.
